Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-08 analysis/paper/paper.Rmd
Add figure title to Figure 2 as per Reviewer 1

# put them all together
p <- (A | B) / (C | D)
p <- p + plot_annotation(tag_levels = "A")
ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("../figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```

>>>>

# put them all together
p <- (A | B) / (C | D)
p <- p + plot_annotation(tag_levels = "A",
                         title = "Aggregated article scores")
ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("../figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```
